Measurement Bias from Address Aliasing

### 2014-11-19 paper.tex
Remove spike 2 column from correlation table
Trim width to fit in one column, compensate by adding a sentence
explaining that the spikes were identical.

There are clearly two worst cases, indicated by significant spikes at the 3184 and 7280 byte offsets.
We sampled an extensive set of performance counters in addition to cycle count for each execution context.
To analyze the bias effects at these points, we calculate the \emph{median} value of each counter over all contexts, and compare that to the two extreme cases.
Going through the list of events manually, we selected the set that had the highest correlation with cycle count.
Table \ref{tab:loopcorrelation} shows numerical counter values for these cases, compared to the median values.

% Detailed comparison between median and worst cases.
\begin{table}
  \caption{Events with significant correlation to cycle count.\label{tab:loopcorrelation}}{
    \pgfplotstabletypeset[
      int detect, % Output whole numbers for counter values
      col sep=comma,
      columns={Performance counter, Median, [index]3, [index]4},
      column type=r,
      columns/Performance counter/.style={
        string type, 
        column type=l,
        column type/.add={|}{},
        postproc cell content/.append code={
          \pgfkeysalso{@cell content=\perfctr{##1}}
        }
      },
      every head row/.style={
        output empty row,
        before row={\hline
          Performance counter & Median & Spike 1 & Spike 2 \\
        },
        after row=\hline\hline
      },
      every last row/.style={after row=\hline},
      every last column/.style={column type/.add={}{|}}
    ]{bin/microkernel-comparison-haswell.csv}
  }
% TODO: make this a real note
    {[Note:] Some correlating performance events are omitted, for example bus-cycles which will naturally vary with total cycle count.}
\end{table}

>>>>

There are clearly two worst cases, indicated by significant spikes at the 3184 and 7280 byte offsets.
We sampled an extensive set of performance counters in addition to cycle count for each execution context.
To analyze the bias effects at these points, we calculate the \emph{median} value of each counter over all contexts, and compare that to the two extreme cases.
Going through the list of events manually, we selected the set that had the highest correlation with cycle count\footnote{Some correlating performance events are omitted; for example bus-cycles, which will naturally vary with total cycle count.}.
Table \ref{tab:loopcorrelation} shows numerical counter values for the first spike, compared to the median values. Event counts on the second spike are virtually identical to the first, and omitted for brevity.

% Detailed comparison between median and worst cases.
\begin{table}
  \caption{Events with significant correlation to cycle count.\label{tab:loopcorrelation}}
  \pgfplotstabletypeset[
    int detect, % Output whole numbers for counter values
    col sep=comma,
    columns={Performance counter, Median, [index]3}, %, [index]4
    column type=r,
    columns/Performance counter/.style={
      string type, 
      column type=l,
      column type/.add={|}{},
      postproc cell content/.append code={
        \pgfkeysalso{@cell content=\perfctr{##1}}
      }
    },
    every head row/.style={
      output empty row,
      before row={\hline
        Performance counter & Median & Spike \\ % & Spike 2
      },
      after row=\hline\hline
    },
    every last row/.style={after row=\hline},
    every last column/.style={column type/.add={}{|}}
  ]{bin/microkernel-comparison-haswell.csv}
\end{table}
